SSA based global code motion of identical computations

### 2017-04-15 acmart-pacmpl-template.tex
liveness

\subsection{Liveness using DJ Graph}
DJ-Graph \cite{Sreedhar1996} is a data structure that augments the dominator
tree with join-edges to keep track of data-flow in a program. We use DJ-Graph to
compute liveness of variables as illustrated in \cite{das2012}.  It is very
efficient for computing liveness because the values will only flow either
through dominator edges or the join edges (where we insert a PHI).

>>>>

\subsection{Liveness using DJ Graph}
DJ-Graph \cite{Sreedhar1996} is a data structure that augments the dominator
tree with join-edges to keep track of data-flow in a program. We use DJ-Graph
and Merge Sets to compute liveness of variables as illustrated in
\cite{das2012}.  It is very efficient for computing liveness and does not
require any bitvectors to be maintained for each basic block. The underlying
simplicity of liveness computation is due to SSA form, where the the values only
flow (from def to use) either through dominator edges or the join edges (where
we insert a PHI). The DJ-graph contains both these edges which allows for
computation of merge sets for each basic block i.e., a set of all basic blocks
where the values can flow from a particular basic block.

We compute merge sets of the control flow graph which remains
same through the code-motion transformation. For code-motion we only want to
know if a use operand is a kill (to compute changes in register pressure). For
that we only need to know whether the use is also required later in the
execution path. A variable is live out of a basic block B if it is used in the
merge set of B. We compute the live-out relation on-demand when profitability of
hoistable/sinkable candidates is to be evaluated.
